Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-13 manuscript/manuscript.tex
responded to some comments

Despite its widespread use, the KS test can be 
misapplied when its foundational assumptions are overlooked. The KS test 
assumes the data are independently and identically distributed and 
that the hypothesized distribution is continuous and fully specified without 
the need for parameter estimation. \citet{zeimbekakis2022misuses} examines
common misapplications of the one-sample KS test. One notable inappropriate
use is when the hypothesized distribution contains unspecified parameters.
In this case, the tests are generally constructed by substituting the unknown
parameters by their estimates, and the asymptotic null distribution of
the test statistic may depend in a complex way on the unknown parameters.
The problem of unspecified parameters can be handled by a parametric
bootstrap, where bootstrap samples of the test statistics are constructed from
samples generated from the fitted hypothesized distribution.
Alternatively, \citet{babu2004goodness} address this issue through a
nonparametric bootstrap method that corrects the bias in the asymptotic null
distribution.

Another prevalent misapplication of the KS test arises when data exhibit serial
dependence, which is often overlooked in analyses. For example, in an
investigation of performance variation in high-performance computing systems,
\citet{tuncer2019ieee} did not describe how or if they accounted for serial
dependence when applying the two-sample KS test.
A particularly complex scenario arises when the distribution has unspecified
parameters, and the data are serially dependent.
The distribution of the test statistic under the null hypothesis depends on both
the unknown parameters and unknown serial dependence. 
\citet{zeimbekakis2022misuses} recommend a semiparametric bootstrap
approach, where the parameters of the hypothesized distribution and the serial
dependence both need to be estimated and their uncertainty accounted for.
Nonetheless, if the working dependence model is too far from the truth, the
results of the tests would not be reliable. For this reason, a nonparametric
method that does not specify the serial dependence is desired.

Developing a fully nonparametric solution for the KS 
tests in the presence of serially dependent data presents a significant 
challenge. The null distribution's characteristics are intricately linked to 
the structure of the serial dependence, which can vary widely in practical 
situations. Employing a nonparametric bootstrap would necessitate defining a 
specific model for this dependence, despite the primary focus being on 
evaluating the marginal distribution of a stationary series. To date, a bias 
correction method for block bootstrap, akin to the nonparametric bootstrap
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks 
to bridge this gap by introducing a bias correction technique for the 
nonparametric block bootstrap, tailored for use in scenarios where the 
hypothesized distribution has unspecified parameters and the data 
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent.

The remainder of this paper is structured as follows: 
Section~\ref{sec:methods} provides an overview of the block bootstrap 
procedure and introduces the bias correction methodology for the 
nonparametric block bootstrap KS test. Section~\ref{sec:simu} is divided 
into two parts; initially, we evaluate the KS test's ability to maintain 
its size, i.e., its consistency in not rejecting the null hypothesis when 
it is indeed true. Subsequently, we examine the test's power, assessing 
whether it can reject the null hypothesis when it is false. Practical 
applications of our method are presented in Section~\ref{sec:real}, where 
we apply the approach to analyze if S\&P 500 index stock return
data adheres to either the Normal or the Student's $t$ distribution. The 
paper concludes with Section~\ref{sec:conclusion}, offering final thoughts
and remarks.

@@

\eds{Please check consistency with how you refer to $F$.  In 
Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
parameter arguments are separated by a semicolon.  At the beginning of 
Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
separating the data argument from the parameter argument (and no 0 subscript
either).   Then in this first 
subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
arguments.  Then immediately above its use is mixed with $F(x)$ without a 
parameter argument (implying it is the true parameter $\theta$). This continues
throughout the document. I suggest either using consistent notation throughout, 
or explicitly defining any shortened/simplified notation at its first use.}

@@

\subsection{Nonparametric bootstrap for independent data}

@@

In summary, the procedure of the nonparametric bootstrap KS test for independent
sample is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying basic bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.  
	\eds{$F_\theta$ has not yet been defined.}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
  bias term.
\end{enumerate}

@@

\subsection{Nonparametric block bootstrap for stationary series}

@@

Continuing using the notation in the independent case,
we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
the estimated parameters based on the $b$th bootstrap sample,
$b = 1, \ldots, B$.
We then use block bootstrap to approximate the asymptotic distribution of
the KS statistic under $H_0$. In particular, we
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x))$, and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ as
an approximation of the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$.
The expected values $E[F^{(b)}_n(x)]$ and
$E[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
$E_n[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
$E_n[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.

@@

\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
the $E(\cdot)$ above and below?}

In summary, the procedure of the nonparametric block bootstrap test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values $p_r$
for the test when applied to samples from the same data generating process.
\eds{I assume $r$ is for replicate?  Please define and include how many 
total replicates you are using.}

@@

Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
plots of the p-values testing the marginal distribution of the stationary time
series generated from the null hypothesis, created with R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line. The plots suggest that the extent to which the p-values are
uniformly distributed is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally 
\eds{uniformly?} distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

\begin{table}[tbp]
\centering
\caption{Rejection rates for test that sample follows its true
                    distribution family for
                   different values of AR(1) coefficient and for different 
                   significance levels.
		\eds{Not sure if it will help presentation or interpretation, but you could
	consider presenting the values inside the table as estimated size/true size}}
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 0.052 & 0.013& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
& {200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
& {400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
& {800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\
  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
  & {200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
  & {400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
  & {800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

Using the \textsl{tseries} package \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices. 
It is known as stylized facts that daily return series often exhibit nonlinear
dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
  cont2001empirical}. The lag-1 Kendall's $\tau$ of the series is
about $-0.0298$, indicating a fairly weak serial linear correlation, but
certainly not meaning absence of serial dependence.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
with the proposed nonparametric block bootstrap (NPBB) method.
\eds{Introduce this acronym earlier (as early as in the intro), and use it 
throughout the ms.}
For comparison, we tested the same hypotheses using 1) the
semiparametric bootstrap (SPB) method of \citet{zeimbekakis2022misuses},
which accounts for both serial dependence and unspecified parameters;
2) nonparametric bootstrap (NPB) bias correction method of
\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
The p-values for these tests are summarized in 
Table~\ref{table:SP5004}.

\begin{table}[ht]
\centering
\caption{P-values for 4 years of S\&P 500 stock return 
  data using different durations
  and different degrees of freedom for Student's $t$ distribution.
	\eds{how are ``different durations'' reflected in this table?}
  NPBB: nonparametric block bootstrap;
  SPB: semiparametric bootstrap;
  NPB: nonparametric bootstrap;
  PB: parametric bootstrap.} 
\label{table:SP5004}
\begin{tabular}{ccccc}
  \toprule
$\nu$ & NPBB & SPB & NPB & PB\\ 
  \midrule
$\infty$ & 0.0001 & 0.0000 & 0.0000 & 0.0000 \\ 
  30 & 0.0019 & 0.0000 & 0.0000 & 0.0000 \\ 
  20 & 0.0027 & 0.0000 & 0.0000 & 0.0000 \\ 
  10 & 0.0125 & 0.0002 & 0.0003 & 0.0003 \\ 
  5 & 0.0610 & 0.0192 & 0.0222 & 0.0141 \\ 
  4 & 0.1037 & 0.0733 & 0.0574 & 0.0499 \\ 
  3 & 0.3133 & 0.3000 & 0.2759 & 0.2686 \\ 
  2 & 0.0418 & 0.0461 & 0.0377 & 0.0443 \\ 
  1 & 0.0000 & 0.0000 & 0.0000 & 0.0000 \\ 
  \bottomrule
\end{tabular}
\end{table}

@@

The KS test remains a crucial tool for researchers across diverse fields,
enabling critical assessments of population distributions. We introduced a
nonparametric block bootstrap variant of the KS test tailored for data with
serial dependencies, which eliminates the need for explicit modeling serial
dependence in addition to parameter specification within the hypothesized
distribution. Our simulations have demonstrated that, given
sufficiently large samples of time series data and moderate serial dependencies,
the test maintains its size under the null hypothesis and have considerable
power in detecting deviations from the hypothesized marginal distribution. The
method's performance improves as the strength of temporal dependence decreases
or the sample size increases. For moderate serial dependence levels in practice,
the test can be recommended for sample size~$n = 400$ or higher.
Overall, the test provides an analog of the bias-corrected nonparametric
bootstrap KS test of \citet{babu2004goodness} in the context of stationaly time
series with unspecified serial dependence. Compared to the semiparametric method
of \citet{zeimbekakis2022misuses}, which requires a working dependence model, it
is reliable regardless of whether the working dependence model approximates the
true dependence model.

>>>>

Despite its widespread use, the KS test can be 
misapplied when its foundational assumptions are overlooked. The KS test 
assumes the data are independently and identically distributed and 
that the hypothesized distribution is continuous and fully specified without 
the need for parameter estimation. \citet{zeimbekakis2022misuses} examines
common misapplications of the one-sample KS test. One notable inappropriate
use is when the hypothesized distribution contains unspecified parameters.
In this case, the tests are generally constructed by substituting the unknown
parameters by their estimates, and the asymptotic null distribution of
the test statistic may depend in a complex way on the unknown parameters.
The problem of unspecified parameters can be handled by a parametric
bootstrap, where bootstrap samples of the test statistics are constructed from
samples generated from the fitted hypothesized distribution.
Alternatively, \citet{babu2004goodness} address this issue through a
nonparametric bootstrap (NPB) method that corrects the bias in the asymptotic null
distribution.

Another prevalent misapplication of the KS test arises when data exhibit serial
dependence, which is often overlooked in analyses. For example, in an
investigation of performance variation in high-performance computing systems,
\citet{tuncer2019ieee} did not describe how or if they accounted for serial
dependence when applying the two-sample KS test.
A particularly complex scenario arises when the distribution has unspecified
parameters, and the data are serially dependent.
The distribution of the test statistic under the null hypothesis depends on both
the unknown parameters and unknown serial dependence. 
\citet{zeimbekakis2022misuses} recommend a semiparametric bootstrap (SPB)
approach, where the parameters of the hypothesized distribution and the serial
dependence both need to be estimated and their uncertainty accounted for.
Nonetheless, if the working dependence model is too far from the truth, the
results of the tests would not be reliable. For this reason, a nonparametric
method that does not specify the serial dependence is desired.

Developing a fully nonparametric solution for the KS 
tests in the presence of serially dependent data presents a significant 
challenge. The null distribution's characteristics are intricately linked to 
the structure of the serial dependence, which can vary widely in practical 
situations. Employing a nonparametric method would necessitate defining a 
specific model for this dependence, despite the primary focus being on 
evaluating the marginal distribution of a stationary series. To date, a bias 
correction method for block bootstrap, akin to the NPB
approach of \citet{babu2004goodness} for independent data,
has not been established. This study seeks 
to bridge this gap by introducing a bias correction technique for the 
nonparametric block bootstrap (NPBB), tailored for use in scenarios where the 
hypothesized distribution has unspecified parameters and the data 
exhibit serial dependence. Our approach reduces to that of
\citet{babu2004goodness} when the data are independent.

The remainder of this paper is structured as follows: 
Section~\ref{sec:methods} provides an overview of the block bootstrap 
procedure and introduces the bias correction methodology for the 
NPBB KS test. Section~\ref{sec:simu} is divided 
into two parts; initially, we evaluate the KS test's ability to maintain 
its size, i.e., its consistency in not rejecting the null hypothesis when 
it is indeed true. Subsequently, we examine the test's power, assessing 
whether it can reject the null hypothesis when it is false. Practical 
applications of our method are presented in Section~\ref{sec:real}, where 
we apply the approach to analyze if S\&P 500 index stock return
data adheres to either the Normal or the Student's $t$ distribution. The 
paper concludes with Section~\ref{sec:conclusion}, offering final thoughts
and remarks.

@@

\eds{Please check consistency with how you refer to $F$.  In 
Equation~\eqref{eq:ks_standard}, it is $F(x; \theta_0)$ where the data and 
parameter arguments are separated by a semicolon.  At the beginning of 
Section~\ref{sec:methods}, it is $F(\cdot \mid \theta)$, with the vertical bar
separating the data argument from the parameter argument (and no 0 subscript
either).   Then in this first 
subsection it is $F(x; \hat\theta_n)$ with a semicolon separating the two 
arguments.  Then immediately above its use is mixed with $F(x)$ without a 
parameter argument (implying it is the true parameter $\theta$). This continues
throughout the document. I suggest either using consistent notation throughout, 
or explicitly defining any shortened/simplified notation at its first use.}
\mc{I believe the vertical bar is to indicate that the parameters are 
unspecified}

@@

\subsection{Nonparametric bootstrap (NPB) for independent data}

@@

In summary, the procedure of the NPB KS test for independent
sample is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying basic bootstrap 
  on the original sample as
  defined previously.
\item
  Obtain parametrically
  fitted parameters 
	$\hat\theta^{(b)}_n$ of $\theta$ from $X^{(b)}_1,...,X^{(b)}_n$.  
	\eds{$F_\theta$ has not yet been defined.}\mc{addressed}
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(F_n(x) - F(x; \hat\theta_n))$ is the known
  bias term.
\end{enumerate}

@@

\subsection{Nonparametric block bootstrap (NPBB) for stationary series}

@@

Continuing using the notation in the independent case,
we use $F^{(b)}_n$ and $\hat\theta^{(b)}_n$ for the empirical distribution and
the estimated parameters based on the $b$th bootstrap sample,
$b = 1, \ldots, B$.
We then use block bootstrap to approximate the asymptotic distribution of
the KS statistic under $H_0$. In particular, we
use the distribution of $\sqrt{n}(F^{(b)}_n(x) - E[F^{(b)}_n(x)])$
as an approximation of the distribution of
$\sqrt{n}(F_n(x) - F(x))$, and the distribution of 
$\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E[\hat\theta^{(b)}_n]))$ as
an approximation of the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$.
The expected values $E[F^{(b)}_n(x)]$ and
$E[\hat\theta^{(b)}_n]$ can be approximated by, respectively,
$E[F^{(b)}_n(x)] = \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$ and
$E[\hat\theta^{(b)}_n]  =  \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.

@@

\eds{Do we not define $Y^{(b)}_n(x)$ in terms of the $E_n(\cdot)$'s instead of 
the $E(\cdot)$ above and below?}\mc{$E_n$ was a typo}

In summary, the procedure of the NPBB test is 
summarized as follows. Repeat the following steps for $b \in \{1, ..., B\}$.
\begin{enumerate}
\item
  Generate $X^{(b)}_1,...,X^{(b)}_n$ by applying moving block bootstrap 
  on the original sample as
  defined previously.
\item
  Fit $F_\theta$ to $X^{(b)}_1,...,X^{(b)}_n$ and obtain estimate 
	$\hat\theta^{(b)}_n$ of $\theta$.
\item
  Obtain the empirical distribution function $F^{(b)}_n$ of
  $X^{(b)}_1,...,X^{(b)}_n$. 
\item
  Calculate bootstrap KS statistic
  \[
    T^{(b)}_n = \sup_x | \sqrt{n}\left(F^{(b)}_n(x) 
    - F(x; \hat\theta^{(b)}_n)\right) - B_n(x) |.
  \]
  where 
  $B_{n}(x) = \sqrt{n}(E[F^{(b)}_n(x)] - 
  F(x; E[\hat\theta^{(b)}_n]))$ is the known
  bias term.
\end{enumerate}

@@

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions 
are very similar and their
first two moments are the same. 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution is from the
Normal family, or 
$X_t \sim N(\cdot \mid \mu, \sigma^2), \quad t = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_t \sim \Gamma(\cdot \mid \alpha, \beta), \quad t = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$.
\eds{Vertical bar vs semicolon to separate data and parameter arguments.}
\mc{I believe the vertical bar is indicate that the parameter arguments are 
unspecified}
For the block
bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 1000\}$
for the test when applied to samples from the same data generating process.
\eds{I assume $r$ is for replicate?  Please define and include how many 
total replicates you are using.} \mc{addressed}

@@

Figure~\ref{fig:qq} shows the Quantile-Quantile (Q-Q)
plots of the p-values testing the marginal distribution of the stationary time
series generated from the null hypothesis, created with R packages
\textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2}. If the
distribution of the p-values is uniform, the points will be aligned with the
diagonal line. The plots suggest that the extent to which the p-values are
uniformly distributed is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be uniformly
\eds{uniformly?}\mc{addressed} distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

\begin{table}[tbp]
\centering
\caption{Rejection rates or true size for test that sample follows its true
                    distribution family for
                   different values of AR(1) coefficient and for different 
                   significance levels or estimated sizes.
		\eds{Not sure if it will help presentation or interpretation, but you could
	consider presenting the values inside the table as estimated size/true size}
	\mc{addressed}}
\label{table:size}
\begin{tabular}{lllrrrrrrr}
  \toprule
$F(\cdot; \theta)$ & $n$ & $\alpha$ & $\tau = -0.75$ & $\tau = -0.5$ & $\tau = -0.25$ 
& $\tau = 0$ & $\tau = 0.25$ & $\tau = 0.5$ & $\tau = 0.75$ \\ 
  \midrule
{$N(8,8)$} & {100} & 0.01 & 0.052 & 0.013& 0.007 & 0.011 & 0.009 & 0.013 & 0.058 \\ 
& & 0.05 & 0.138 & 0.061 & 0.038 & 0.059 & 0.054 & 0.083 & 0.178 \\ 
& & 0.10 & 0.238 & 0.125 & 0.089 & 0.124 & 0.102 & 0.152 & 0.272 \\ 
& {200} & 0.01 & 0.043 & 0.009 & 0.006 & 0.017 & 0.011 & 0.018 & 0.062 \\ 
& & 0.05 & 0.130 & 0.058 & 0.041 & 0.051 & 0.053 & 0.061 & 0.175 \\ 
& & 0.10 & 0.202 & 0.120 & 0.101 & 0.107 & 0.110 & 0.125 & 0.266 \\ 
& {400} & 0.01 & 0.037 & 0.011 & 0.009 & 0.014 & 0.013 & 0.009 & 0.043 \\ 
& & 0.05 & 0.109 & 0.047 & 0.052 & 0.061 & 0.044 & 0.064 & 0.133 \\ 
& & 0.10 & 0.174 & 0.099 & 0.098 & 0.108 & 0.099 & 0.123 & 0.212 \\ 
& {800} & 0.01 & 0.023 & 0.011 & 0.008 & 0.011 & 0.011 & 0.011 & 0.038 \\ 
& & 0.05 & 0.088 & 0.043 & 0.040 & 0.055 & 0.042 & 0.053 & 0.125 \\ 
& & 0.10 & 0.166 & 0.097 & 0.095 & 0.102 & 0.107 & 0.109 & 0.196 \\ [1ex]
{$\Gamma(8,1)$} & {100} & 0.01 & 0.056 & 0.014 & 0.006 & 0.011 & 0.009 & 0.015 & 0.063 \\
  & & 0.05 & 0.144 & 0.063 & 0.037 & 0.059 & 0.053 & 0.083 & 0.180 \\ 
  & & 0.10 & 0.239 & 0.125 & 0.092 & 0.126 & 0.103 & 0.150 & 0.273 \\ 
  & {200} & 0.01 & 0.045 & 0.012 & 0.005 & 0.017 & 0.012 & 0.020 & 0.066 \\ 
  & & 0.05 & 0.127 & 0.058 & 0.045 & 0.052 & 0.054 & 0.056 & 0.173 \\ 
  & & 0.10 & 0.204 & 0.123 & 0.103 & 0.106 & 0.108 & 0.129 & 0.263 \\ 
  & {400} & 0.01 & 0.038 & 0.012 & 0.010 & 0.014 & 0.010 & 0.010 & 0.045 \\ 
  & & 0.05 & 0.106 & 0.049 & 0.051 & 0.062 & 0.042 & 0.063 & 0.128 \\ 
  & & 0.10 & 0.175 & 0.097 & 0.098 & 0.107 & 0.100 & 0.122 & 0.211 \\ 
  & {800} & 0.01 & 0.024 & 0.011 & 0.007 & 0.011 & 0.011 & 0.010 & 0.039 \\ 
  & & 0.05 & 0.089 & 0.043 & 0.041 & 0.055 & 0.044 & 0.051 & 0.121 \\ 
  & & 0.10 & 0.169 & 0.096 & 0.094 & 0.100 & 0.109 & 0.110 & 0.194 \\ 
   \bottomrule
\end{tabular}
\end{table}

@@

Using the \textsl{tseries} package \citep{tseries}, 
we gathered daily closing prices for the S\&P 500 index from January 1st, 2020
to December 31st, 2023. Daily returns were obtained by taking the difference in
the logarithm of the closing prices. 
It is known as stylized facts that daily return series often exhibit nonlinear
dependence and unconditional heavy tails \citep[e.g.,][]{ryden1998stylized,
  cont2001empirical}. The lag-1 Kendall's $\tau$ of the series is
about $-0.0298$, indicating a fairly weak serial linear correlation, but
certainly not meaning absence of serial dependence.
Using our method, we tested that the daily returns are normally
distributed and Student's $t$ distributed 
with degrees of freedom $\nu \in \{30, 20, 10, 5, 4, 3, 2, 1\}$
with the proposed NPBB method.
\eds{Introduce this acronym earlier (as early as in the intro), and use it 
throughout the ms.}\mc{addressed}
For comparison, we tested the same hypotheses using 1) the
SPB method of \citet{zeimbekakis2022misuses},
which accounts for both serial dependence and unspecified parameters;
2) NPB bias correction method of
\citet{babu2004goodness}; and and 3) the parametric bootstrap (PB) method shown
by \citet{zeimbekakis2022misuses}. The latter of the two methods discard the
serial dependence. In all methods, we used $B = 10,000$ bootstrap replicates.
The p-values for these tests are summarized in 
Table~\ref{table:SP5004}.

\begin{table}[ht]
\centering
\caption{P-values for 4 years of S\&P 500 stock return 
  data using different degrees of freedom for Student's $t$ distribution.
	\eds{how are ``different durations'' reflected in this table?}\mc{addressed}
  NPBB: nonparametric block bootstrap;
  SPB: semiparametric bootstrap;
  NPB: nonparametric bootstrap;
  PB: parametric bootstrap.} 
\label{table:SP5004}
\begin{tabular}{ccccc}
  \toprule
$\nu$ & NPBB & SPB & NPB & PB\\ 
  \midrule
$\infty$ & 0.0001 & 0.0000 & 0.0000 & 0.0000 \\ 
  30 & 0.0019 & 0.0000 & 0.0000 & 0.0000 \\ 
  20 & 0.0027 & 0.0000 & 0.0000 & 0.0000 \\ 
  10 & 0.0125 & 0.0002 & 0.0003 & 0.0003 \\ 
  5 & 0.0610 & 0.0192 & 0.0222 & 0.0141 \\ 
  4 & 0.1037 & 0.0733 & 0.0574 & 0.0499 \\ 
  3 & 0.3133 & 0.3000 & 0.2759 & 0.2686 \\ 
  2 & 0.0418 & 0.0461 & 0.0377 & 0.0443 \\ 
  1 & 0.0000 & 0.0000 & 0.0000 & 0.0000 \\ 
  \bottomrule
\end{tabular}
\end{table}

@@

The KS test remains a crucial tool for researchers across diverse fields,
enabling critical assessments of population distributions. We introduced a
NPBB variant of the KS test tailored for data with
serial dependencies, which eliminates the need for explicit modeling serial
dependence in addition to parameter specification within the hypothesized
distribution. Our simulations have demonstrated that, given
sufficiently large samples of time series data and moderate serial dependencies,
the test maintains its size under the null hypothesis and have considerable
power in detecting deviations from the hypothesized marginal distribution. The
method's performance improves as the strength of temporal dependence decreases
or the sample size increases. For moderate serial dependence levels in practice,
the test can be recommended for sample size~$n = 400$ or higher.
Overall, the test provides an analog of the bias-corrected NPB KS test of 
\citet{babu2004goodness} in the context of stationaly time
series with unspecified serial dependence. Compared to the SPB method
of \citet{zeimbekakis2022misuses}, which requires a working dependence model, it
is reliable regardless of whether the working dependence model approximates the
true dependence model.
